\vspace*{-8mm}\textbf{\textsc{Novelty Detection for Semantic Place Categorization}}

### 2011-06-26 thesis/novelty-intro.tex
Address final comments by andrzej

\subsection{Probability Ratio Comparison}
%%% Results 1
% Show the threshold ratio is an optimal detector (if perfect information was available)
% Show that the thresholds are suitable functions for implementing a static threshold.
First, the performance of the novelty threshold selection was plotted for a set
of 1000 samples taken from the whole distribution (\autoref{fig:synthetic-roc}).
Those samples contain different numbers of sensed properties for each room, mimicking
the dynamic properties expected to see when implemented on a robot.

@@

\caption{\label{fig:synthetic-roc}ROC curve comparing the novelty detection performance
         for samples with variable size of sensed properties.}
\end{figure}

The convex shape of the optimal threshold shows that the ratio between conditional
and unconditional probability is indeed an optimal detector \textbf{[Why does it show it's optimal?? Maybe too strong word?]}
and is suitable for implementing a threshold when the samples are taken from dynamic
distributions (e.g.\ some samples where there is only access to room size versus
samples where there is a lot of information about the room properties).

>>>>

\subsection{Probability Ratio Comparison}
%%% Results 1
% Show the threshold ratio is an optimal detector (if perfect information was available)
% Show that the thresholds are suitable functions for implementing a static threshold.
First, the performance of the novelty threshold selection was plotted for a set
of 1000 samples taken from the whole distribution (\autoref{fig:synthetic-roc}).
The samples where uniformly generated by graphs with 5, 10, 15, 20, 35, 50 features.
Additionally the feature types were also uniformly sampling, for that it is possible
that in certain samples some feature types were sensed more than once and other were not
sensed at all.
This was chosen to mimic
the dynamic properties expected to see when implemented on a robot.

@@

\caption{\label{fig:synthetic-roc}ROC curve comparing the novelty detection performance
         for samples with variable number of sensed properties.}
\end{figure}

The convex shape of the optimal threshold shows that the ratio between conditional
and unconditional probability is indeed a suitable detector for implementing a threshold when
the samples are taken from dynamic distributions when $P(novel)$ is constant
(e.g.\ some samples where there is only access to room size versus
samples where there is a lot of information about the room properties).
